Poll-Based Forecasting of the 2024 U.S. Presidential Election

### 2024-11-04 other/literature/ElectionForcast_linearmodel.qmd
merging from branch: Final
merging from branch: Final

# Create a combined data frame for plotting purposes
predictions_df <- data.frame(
  Candidate = c("Donald Trump", "Kamala Harris"),
  Predicted_Support = c(mean(candidate_data$Trump_Predicted_Support, na.rm = TRUE), 
                        mean(candidate_data$Harris_Predicted_Support, na.rm = TRUE))
)

@@

### Prediction and Visualization
```{r}
#| echo: false
#| warning: false
#| message: false
# Adjust the bar plot height
bar_plot <- ggplot(predictions_df, aes(x = Candidate, y = Predicted_Support, fill = Candidate)) +
  geom_bar(stat = "identity", width = 0.6, color = "white") +
  geom_text(aes(label = paste0(round(Predicted_Support, 1), "%")), 
            vjust = -0.5, size = 5) +
  labs(title = "",
       x = "Candidate",
       y = "Predicted Support (%)") +
  theme_minimal() +
  scale_fill_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon")) +
  ylim(0, max(predictions_df$Predicted_Support) * 1.2)  # Set upper limit to make space for labels

@@

# Create the pie chart
pie_chart <- ggplot(pie_data, aes(x = "", y = Support, fill = Candidate)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  labs(title = "") +
  theme_void() +  # Remove background and axis
  theme(legend.position = "right") +
  scale_fill_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon", "Other Candidates" = "grey")) +
  geom_text(aes(label = ifelse(Support > 5, paste0(round(Support, 1), "%"), "")), 
            position = position_stack(vjust = 0.5), color = "white", size = 5)

# Print the pie chart
print(pie_chart)

```

>>>>

# Create a combined data frame for plotting purposes
predictions_df <- data.frame(
  Candidate = c("Donald Trump", "Kamala Harris"),
  Predicted_Support = c(
    mean(candidate_data$Trump_Predicted_Support, na.rm = TRUE),
    mean(candidate_data$Harris_Predicted_Support, na.rm = TRUE)
  )
)

@@

### Prediction and Visualization
```{r}
#| echo: false
#| warning: false
#| message: false
# Adjust the bar plot height
bar_plot <- ggplot(predictions_df, aes(x = Candidate, y = Predicted_Support, fill = Candidate)) +
  geom_bar(stat = "identity", width = 0.6, color = "white") +
  geom_text(aes(label = paste0(round(Predicted_Support, 1), "%")),
    vjust = -0.5, size = 5
  ) +
  labs(
    title = "",
    x = "Candidate",
    y = "Predicted Support (%)"
  ) +
  theme_minimal() +
  scale_fill_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon")) +
  ylim(0, max(predictions_df$Predicted_Support) * 1.2) # Set upper limit to make space for labels

@@

# Create the pie chart
pie_chart <- ggplot(pie_data, aes(x = "", y = Support, fill = Candidate)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  labs(title = "") +
  theme_void() + # Remove background and axis
  theme(legend.position = "right") +
  scale_fill_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon", "Other Candidates" = "grey")) +
  geom_text(aes(label = ifelse(Support > 5, paste0(round(Support, 1), "%"), "")),
    position = position_stack(vjust = 0.5), color = "white", size = 5
  )

# Print the pie chart
print(pie_chart)
```

### 2024-11-04 paper/paper.qmd
merging from branch: Final
merging from branch: Final

---
title: "Poll-Based Forecasting of the 2024 U.S. Presidential Election"
subtitle: "Valid Multiple Linear Regression Explains Why Kamala Harris Will Win"
author: 
  - Haowei Fan
  - Fangning Zhang
  - Shaotong Li
thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
date: today
date-format: long
abstract: "The United States plays a major role in the global technological and economic landscape, with its political leadership having a significant influence on international technology cooperation and economic relations. This project uses multiple linear regression to predict the outcome of the 2024 U.S. presidential election by extracting and analyzing polling data from polls that nominated the same candidates, providing insights to help stakeholders prepare for potential shifts in U.S. policies. The project predicts that Kamala Harris will secure 47.6% of the vote over Donald Trump's 43.5% and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
format: pdf
toc-depth: 2    
number-sections: true
toc: true           
toc-title: "Table of Contents" 
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####
install.packages("tidyverse")
library(tidyverse)
install.packages("knitr")
library(knitr)
install.packages("dplyr")
library(dplyr)
install.packages("arrow")
library(arrow)
install.packages("patchwork")
library(patchwork)
install.packages("car")
library(car)
install.packages("kableExtra")
library(kableExtra)
install.packages("gridExtra")
library(gridExtra)
install.packages("moments")
library(moments)
install.packages("grid")
library(grid)
set.seed(912)
#### Read data ####
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
test_Trump <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
test_Harris <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
full_Trump <- read_parquet(here::here("data/02-analysis_data/00-full/full_Trump.parquet"))
full_Harris <- read_parquet(here::here("data/02-analysis_data/00-full/full_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))
Harris_model <- readRDS(here::here("models/Harris_model.rds"))
```

>>>>

---
title: "Poll-Based Forecasting of the 2024 U.S. Presidential Election"
subtitle: "Valid Multiple Linear Regression Explains Why Kamala Harris Will Win"
author: 
  - Haowei Fan
  - Fangning Zhang
  - Shaotong Li
thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
date: today
date-format: long
abstract: "The United States plays a major role in the global technological and economic landscape, with its political leadership having a significant influence on international technology cooperation and economic relations. This project uses multiple linear regression to predict the outcome of the 2024 U.S. presidential election by extracting and analyzing polling data from polls that nominated the same candidates, providing direction to help stakeholders prepare for potential shifts in U.S. policies. The project predicts that Kamala Harris will secure 47.6% of the vote over Donald Trump's 43.5% and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
format: pdf
toc-depth: 2    
number-sections: true
toc: true           
toc-title: "Table of Contents" 
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Install packages ####
required_packages <- c("tidyverse","knitr","dplyr","arrow","patchwork","car","kableExtra","gridExtra","moments")
for (pkg in required_packages) {
  if (!requireNamespace(pkg,quietly = TRUE)) {
    install.packages(pkg)
  }
}

```

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####

library(tidyverse)

library(knitr)

library(dplyr)

library(arrow)

library(patchwork)

library(car)

library(kableExtra)

library(gridExtra)

library(moments)

library(grid)
set.seed(912)
#### Read data ####
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
test_Trump <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
test_Harris <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
full_Trump <- read_parquet(here::here("data/02-analysis_data/00-full/full_Trump.parquet"))
full_Harris <- read_parquet(here::here("data/02-analysis_data/00-full/full_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))
Harris_model <- readRDS(here::here("models/Harris_model.rds"))
```
